---
title: Analysis
description:
toc: true
featuredVideo:
featuredImage: 
draft: false
---

This comes from the file `content/analysis.Rmd`.

We describe here our detailed data analysis


## Introduce what motivates your Data Analysis (DA)

We are most interested in investigating how CO2 emissions relate to our crop data. We are curious as to whether crop production, area harvested, and area planted impact emission data. We're investigating the question "does farming impact CO2 emissions?"

## Breadth of the DA


## Depth of the DA

```{r packages, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
#install.packages("forecast")
require(forecast)
library(readr)
```

```{r cleaning_data, echo=FALSE}
## CLEAN THE DATA
co2_data_clean <- read.csv(here::here("dataset/clean_co2.csv"))

for(i in 2:ncol(co2_data_clean)){
  co2_data_clean[,i][(co2_data_clean[,i]==0)] = mean(co2_data_clean[,i])
}

```

```{r correlations}
#Correlation matrix of all variables with all other variables
res = cor(co2_data_clean[2:13])
res

#Correlation of all other variables with CO2 emissions
cor(co2_data_clean[,-1], co2_data_clean$CO2_emissions_kt)

#plot of correlation: heatmap
heatmap(res)

```

