---
title: Barley Analysis
description:
toc: true
featuredVideo:
featuredImage: 
draft: false
---
 
This comes from the file `content/barley_analysis.Rmd`.

```{r packages, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
#install.packages("forecast")
require(forecast)
library(readr)
library(tidyr)
```

```{r load_co2_data, echo=FALSE}
## CLEAN THE DATA
co2_data_clean <- read.csv(here::here("dataset/clean_co2.csv"))

```


```{r barley_co2_dataset, echo=FALSE}
barley_data_3 <- read_csv(here::here("dataset", "barley/crop_p015_t005.csv"),skip = 5)
barley_data_3<- barley_data_3[-2,3:ncol(barley_data_3)] %>% drop_na(Year) %>% head(-1)

barley_data_4 <- read_csv(here::here("dataset", "barley/crop_p016_t010.csv"),skip = 5)
barley_data_4<- barley_data_4[-2,3:ncol(barley_data_4)] %>% drop_na(Year) %>% head(-1)

barley_data <- barley_data_3%>%bind_rows(barley_data_4) 
barley_data <- barley_data %>% type_convert()

barley_co2_data <- co2_data_clean %>% left_join(barley_data, by = c("Time" = "Year"))

#barley_co2_data <- barley_co2_data %>% filter(CO2_emissions_kt != "..") %>% type_convert()
View(barley_co2_data)


#write_csv(barely_co2_data, file = here::here("dataset", "barley_co2_data"))

#save(barley_co2_data, file = here::here("dataset/barely_co2_data.RData"))
```

```{r barley_timeseries}
# read_csv(here::here("dataset/barley_co2_data"))

Year <- barley_co2_data %>% pull(Time)
Production <- barley_co2_data %>% pull(Production)
co_emit <- barley_co2_data %>% pull(CO2_emissions_kt)

barley_ts <- ggplot(barley_co2_data, aes(x=Year, y=Production)) +
  geom_line() +
  xlab("")
barley_ts

```
The above line graph shows barley production in United States from 1990 to 2021. Over the year last 20 years, we can see a clear net downward trend in barley production.




```{r,1}
barley_co2_data %>% ggplot(aes(x = `Area harvested`, y = (CO2_emissions_kt))) + geom_point() + geom_smooth()
barley_co2_data %>% ggplot(aes(x = `Production`, y = (CO2_emissions_kt))) + geom_point() + geom_smooth()
barley_co2_data %>% ggplot(aes(x = `Area planted`, y = (CO2_emissions_kt))) + geom_point() + geom_smooth()
barley_co2_data %>% ggplot(aes(x = `Yield per acre`, y = (CO2_emissions_kt))) + geom_point() + geom_smooth()

```
We explored different variables and factors to conclude that there seems to be no strong relationship between the co2 emission and area harvested, production, area planted, or yield per acre. 

```{r,2}
diff_df <- data.frame(diff_area = diff(barley_co2_data$`Area harvested`), diff_co2 = diff(barley_co2_data$CO2_emissions_kt) )
diff_df %>% ggplot(aes(y = diff_area, x = diff_co2)) + geom_point()+ geom_smooth()
```
There seems to be a weak correlation between diff data. We are using diff to compute the difference between pairs of consecutive elements of co2 emission and barely area harvest. We trying to figure out if the difference between them is significant.  The relation seems to be cubic and not significant. 

```{r,3}
lm1 <- (lm(`Area harvested`~ CO2_emissions_kt, barley_co2_data)) 
summary(lm1)

lm1_diff <-lm(diff_area ~ poly(diff_co2,3), diff_df)
summary(lm1_diff)

```
The R^2 value is 0.04049, so in other words, area harvested for barley accounts for 4% of variation in co2 outputs. Thus there no relationship between area harvested and co2 emission.



