---
title: Barley Analysis
description:
toc: true
featuredVideo:
featuredImage:
draft: false
---
 
This comes from the file `content/barley_analysis.Rmd`.

Here we analyze the relationship between the barley data and the CO2 data.

```{r packages, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
#install.packages("forecast")
require(forecast)
library(readr)
library(tidyr)
```

```{r load_co2_data, echo=FALSE}
## CLEAN THE DATA
co2_data_clean <- read.csv(here::here("dataset/clean_co2.csv"))

```


```{r barley_co2_dataset, echo=FALSE}
barley_data_3 <- read_csv(here::here("dataset", "barley/crop_p015_t005.csv"),skip = 5)
barley_data_3<- barley_data_3[-2,3:ncol(barley_data_3)] %>% drop_na(Year) %>% head(-1)

barley_data_4 <- read_csv(here::here("dataset", "barley/crop_p016_t010.csv"),skip = 5)
barley_data_4<- barley_data_4[-2,3:ncol(barley_data_4)] %>% drop_na(Year) %>% head(-1)

barley_data <- barley_data_3%>%bind_rows(barley_data_4) 
barley_data <- barley_data %>% type_convert()

barley_co2_data <- co2_data_clean %>% left_join(barley_data, by = c("Time" = "Year"))

#barley_co2_data <- barley_co2_data %>% filter(CO2_emissions_kt != "..") %>% type_convert()
View(barley_co2_data)


#write_csv(barely_co2_data, file = here::here("dataset", "barley_co2_data"))

#save(barley_co2_data, file = here::here("dataset/barely_co2_data.RData"))
```

## Barley vs. CO2 Preliminary Analyses
```{r barley_timeseries}
# read_csv(here::here("dataset/barley_co2_data"))

Year <- barley_co2_data %>% pull(Time)
Production <- barley_co2_data %>% pull(Production)
co_emit <- barley_co2_data %>% pull(CO2_emissions_kt)

barley_ts <- ggplot(barley_co2_data, aes(x=Year, y=Production)) +
  geom_line() +
  xlab("")
barley_ts

```
The above line graph shows barley production in United States from 1990 to 2021. Over the year last 20 years, we can see a clear net downward trend in barley production.


```{r,1}
barley_co2_data %>% ggplot(aes(x = `Area harvested`, y = (CO2_emissions_kt))) + geom_point() + geom_smooth()
barley_co2_data %>% ggplot(aes(x = `Production`, y = (CO2_emissions_kt))) + geom_point() + geom_smooth()
barley_co2_data %>% ggplot(aes(x = `Area planted`, y = (CO2_emissions_kt))) + geom_point() + geom_smooth()
barley_co2_data %>% ggplot(aes(x = `Yield per acre`, y = (CO2_emissions_kt))) + geom_point() + geom_smooth()

```
We explored different variables and factors to conclude that there seems to be no strong relationship between the co2 emission and area harvested, production, area planted, or yield per acre. 


## Barley vs. CO2 Emissions In-Depth
```{r,2}
diff_df <- data.frame(diff_area = diff(barley_co2_data$`Area harvested`), diff_co2 = diff(barley_co2_data$CO2_emissions_kt) )
diff_df %>% ggplot(aes(y = diff_area, x = diff_co2)) + geom_point()+ geom_smooth()
```
There seems to be a weak correlation between diff data. We are using diff to compute the difference between pairs of consecutive elements of co2 emission and barely area harvest. We trying to figure out if the difference between them is significant.  The relation seems to be cubic and not significant. 

```{r,3}
lm1 <- (lm(`Area harvested`~ CO2_emissions_kt, barley_co2_data)) 
summary(lm1)

lm1_diff <-lm(diff_area ~ poly(diff_co2,3), diff_df)
summary(lm1_diff)

```
In the above graph, the harvesting of one acre of land of barley is associated with a 2.433*10-5 increase in CO2 emissions. 

The R^2 value is 0.04049, so in other words, area harvested for barley accounts for 4% of variation in co2 outputs. Thus there is a very weak positive correlation between area harvested and co2 emission.


## Price as a Metric for Demand and Forest Area
```{r demand}
barley_co2_data %>% ggplot(aes(y = (GDP_growth), x = `Price per bushel 1/`)) + geom_point() + geom_smooth()
barley_co2_data %>% ggplot(aes(y = (CO2_emissions_kt), x = `Price per bushel 1/`)) + geom_point() + geom_smooth()
barley_co2_data %>% ggplot(aes(y = (Goods_services_exports), x = `Price per bushel 1/`)) + geom_point() + geom_smooth()
barley_co2_data %>% ggplot(aes(y = (Goods_services_exports), x = (Production))) + geom_point() + geom_smooth()

ggplot(barley_co2_data[which(barley_co2_data$Forest_area_percent>0),],aes(y = (Forest_area_percent), x = `Area harvested`)) + geom_point() + geom_smooth()

```
As discussed in the main analysis page, we decided to use price per bushel as a metric for demand for each crop. We saw on the main analysis page that there was no strong correlation between GDP growth and CO2 emissions. There does not appear to be a strong correlation between demand for barley and GDP growth, nor between demand for barley and CO2 emissions either. 

We were also curious about how the crops impacted goods and serviced exports, but it appears demand and production of barley is not strongly correlated with goods and services exports either.

There was a strong negative correlation between area harvested and forest area percent, which was as we expected. As more land is used for growth and harvesting of barley, there is less land available for forests, so forest area percent decreases.

