---
title: Data
description: 
toc: true
featuredVideo:
featuredImage: 
draft: false
---


As we know, climate change continues to be one of the greatest existential threats to our future and our planet. The three biggest causes of this threat are burning fossil fuels, cutting down forests, and farming livestock which add enormous amounts of greenhouse gases to those naturally occurring in the atmosphere. The topic of combating global warming is currently being discussed widely, with leaders all over the world coming up with solutions to slow down this catastrophe. Our group decided to take a further look into CO2 emissions and other various factors that contribute to this global threat in the past 50 years. We also decided to do further analysis on crop production in the United States to see the connection between certain crops and various climate variables.
 
Climate Change Data: https://databank.worldbank.org/reports.aspx?source=2&series=EN.ATM.CO2E.KT&country=# 

Crop data Pdf: https://downloads.usda.library.cornell.edu/usda-esmis/files/c534fn92g/g158cn09g/zc77tv62q/croptr22.pdf

We created our first dataset by choosing climate variables that we thought were vital contributions from the World Bank. The data from World Bank was collected by GHG Emissions Washington, D.C: World Resources Institute, climatewatchdata.org/ghg-emissions.  This data was compiled for research and policy purposes. Our second dataset, Crop Proudction Dataset, was collected by the USDA for the purpose of creating a reference for data users.
 
Our first dataset includes 12 variables: agriculture, forestry, and fishing value added, irrigated land, machinery and tractors, agricultural methane/nitrous oxide emissions, raw materials exports/imports, crop production index, livestock production index, percent of the rural population, and annual freshwater withdrawals. Our initial findings show that there has been a decline in agricultural land, machinery and tractors, raw materials exports, and percent rural population in the past 50 years in the United States. Conversely, there has been an increase in agricultural methane and nitrous oxide emissions, crop production, livestock production index, and annual freshwater withdrawals. 
Our second dataset contains crop production data for individual crops. The dataset has a lot of specific values for each crop over time, which is better suited for interactive models.

Dataset 1 Variables: 

Country: what country data is from. For our project it is all data from USA
Time: Measures year data was collected in. Data ranges from 1972 to 2021
CO2_emissions_kt: CO2 Emissions in year measured in kilotons
Population_growth_annual_percent: Change in population` growth across the year. Measured as a percentage
Forest_area_percent: Measures percent of country covered by forest area in sq km
Electricity_production: measures total amount of electricity produced in country in kilowatts
Renewable_electricity_output: measures total amount of electricity produced from renewable sources (i.e. non fossil fuels) in country in kilowatts
Total_greenhouse_gas_emissions: measures total greenhouse gas emissions per year for country in kt
GDP_growth: measures annual percent change in GDP of country
Fossil_fuel_energy_consumption: Percentage of total energy consumption that comes from fossil fuels and not from other sources (such as renewables)
Research_development_expenditure: Percentage of GDP spent on research and development
Goods_services_exports: Percentage of GDP from exports of goods and services
Population_density: people per sq. km of land area

Dataset 2 Variables:
Area harvested (1,000 acres)
Area planted (1,000 acres)
Yield per acre (bushels)
Production (1,000 bushels)
Price per bushel (dollars)
Value of production (1,000 dollars)



Clean data code can be found here :https://github.com/sussmanbu/ma4615-fa22-final-project-boston-three-party/blame/master/static/load_and_clean_data.R
co2_data <- read_csv(here::here("dataset", "CSV_fixed_climate_data.csv"))

```{r}

co2_data_clean <- co2_data

write_csv(co2_data_clean, file = here::here("dataset", "clean_co2.csv"))

save(co2_data_clean, file = here::here("dataset/clean_co2.RData"))
```



For our CO2 emission we just cleaned the file and wrote a new csv file.We used here::here function to specify the file path

```{r}

corn_data_3 <-read_csv(here::here("dataset", "corn/crop_p031_t024.csv"),skip = 7)
corn_data_3<- corn_data_3[-2,3:ncol(corn_data_3)] %>% drop_na(Year) %>% head(-1)

corn_data_4 <- read_csv(here::here("dataset", "corn/crop_p032_t034.csv"),skip = 7)
corn_data_4<- corn_data_4[-2,3:ncol(corn_data_4)] %>% drop_na(Year) %>% head(-1)

corn_data <- corn_data_3%>%bind_rows(corn_data_4) %>% type_convert()
```





We had several csv files for each crop. So, we merged two files for each crop starting from 1950 to 1989. We removed the na from the years and skipped unnecessary columns. We did this for each crop. 

There were some differences between each crop csv file. The csv file contained a lot of unnecessary information. Therefore, we skipped those columns. After cleaning the files, we used rbind to bind based on the columns. 


```{r}

rye_dataset_3 <- read_csv("dataset/rye/crop_p170_t101.csv", 
                           col_types = cols(`101` = col_skip(), 
                                            t = col_skip(), `Crop Production Historical Track Records: Released April 11, 2022, by the National Agricultural Statistics Service (NASS), Agricultural Statistics Board, United States Department of Agriculture (USDA).` = col_double(), 
                                            u = col_skip(), ...3 = col_double(), 
                                            `(1,000 acres)...4` = col_double()), 
                           skip = 7)
View(rye_dataset_3)


rye_dataset_4 <- read_csv("dataset/rye/crop_p171_t102.csv", 
                           col_types = cols(`102` = col_skip(), 
                                            t = col_skip(), `Crop Production Historical Track Records: Released April 11, 2022, by the National Agricultural Statistics Service (NASS), Agricultural Statistics Board, United States Department of Agriculture (USDA).` = col_double(), 
                                            u = col_skip(), ...3 = col_double()), 
                           skip = 7)
View(rye_dataset_4)

rye_dataset <- rye_dataset_3%>%bind_rows(rye_dataset_4)
```



Our first dataset on climate change did not have the variables input as “numbers” so we had to go in and reset each numerical cell as a numbers 
