---
title: Flaxseed Analysis
description: 
toc: true
featuredVideo: 
featuredImage: 
draft: false
---

This comes from the file `content/flaxseed_analysis.Rmd`.

```{r packages, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
#install.packages("forecast")
require(forecast)
library(readr)
library(tidyr)
```


```{r cleaning_data, echo=FALSE}
## CLEAN THE DATA
co2_data_clean <- read.csv(here::here("dataset/clean_co2.csv"))

view(co2_data_clean)
```

```{r flaxseed_co2_dataset, echo=FALSE}
# used barley datasets for col names
barley_data_3 <- read_csv(here::here("dataset", "barley/crop_p015_t005.csv"),skip = 5)
barley_data_3<- barley_data_3[-2,3:ncol(barley_data_3)] %>% drop_na(Year) %>% head(-1)

barley_data_4 <- read_csv(here::here("dataset", "barley/crop_p016_t010.csv"),skip = 5)
barley_data_4<- barley_data_4[-2,3:ncol(barley_data_4)] %>% drop_na(Year) %>% head(-1)



flaxseed_data_3 <- read_csv(here::here("dataset", "flaxseed/crop_p086_t049.csv"), 
                            col_types = cols(`49` = col_skip(), t = col_skip(), 
                                             `Crop Production Historical Track Records: Released April 11, 2022, by the National Agricultural Statistics Service (NASS), Agricultural Statistics Board, United States Department of Agriculture (USDA).` = col_double(), 
                                             ...3 = col_double(), u = col_skip()), 
                            skip = 7)
colnames(flaxseed_data_3) <- colnames(barley_data_3)

flaxseed_data_3 <- flaxseed_data_3 %>% drop_na(Year)

# View(flaxseed_data_3)
flaxseed_data_4 <- read_csv(here::here("dataset", "flaxseed/crop_p087_t050.csv"), 
                            col_types = cols(`50` = col_skip(), t = col_skip(), 
                                             `Crop Production Historical Track Records: Released April 11, 2022, by the National Agricultural Statistics Service (NASS), Agricultural Statistics Board, United States Department of Agriculture (USDA).` = col_double(), 
                                             ...3 = col_double(), u = col_skip()), 
                            skip = 7)
colnames(flaxseed_data_4) <- colnames(barley_data_4)

flaxseed_data_4 <- flaxseed_data_4 %>% drop_na(Year)

# View(flaxseed_data_4)
flaxseed_data_3 <- flaxseed_data_3 %>% type_convert()
flaxseed_data <- flaxseed_data_3%>%bind_rows(flaxseed_data_4) 
View(flaxseed_data)

flaxseed_co2_data <- co2_data_clean %>% left_join(flaxseed_data, by = c("Time" = "Year"))


flaxseed_co2_data <- flaxseed_co2_data %>% filter(CO2_emissions_kt != "..") %>% type_convert()

View(flaxseed_co2_data)

```

## Flaxseed vs. CO2 Preliminary Analyses
```{r flaxseed_timeseries}

Year <- flaxseed_co2_data %>% pull(Time)
Production <- flaxseed_co2_data %>% pull(Production)
co_emit <- flaxseed_co2_data %>% pull(CO2_emissions_kt)

flaxseed_ts <- ggplot(flaxseed_co2_data, aes(x=Year, y=Production)) +
  geom_line() +
  xlab("")
flaxseed_ts

```

In our time series analysis above, we analyze the production of flaxseed over time.The production of flaxseed peaks around the year 2005. Then it drastically went down. 



```{r,2}
flaxseed_co2_data <- flaxseed_co2_data %>% mutate(t = c(1:nrow(flaxseed_co2_data)))
lm2 <- (lm(`Area harvested`~ CO2_emissions_kt +  I(CO2_emissions_kt^2) + t,  flaxseed_co2_data)) 
summary(lm2)

```
As c02 emission increases the area harvested decreases. This allows us to create an ACF model. We will be adjusting the model to show autocorrelation. P values are statistically significant and there strong positive relationship. 

```{r,3}
flaxseed_co2_data %>% ggplot(aes(x = `Area harvested`, y = CO2_emissions_kt)) + geom_point()+ geom_smooth()

```
 
From this plot we see a strong non-linear correlation between the Area harvest and co2 emission. As the Co2 emission increases the flaxseed area harvest decrease. We further analyze this relationship


```{r,4}
ggAcf(lm2$residuals)
```
Again the high correlation and the ggAcf of residuals show there is no autocorrelation. This allows us to create a prediction model

```{r}
flaxseed_co2_data <- flaxseed_co2_data %>% mutate(t = c(1:nrow(flaxseed_co2_data)))
lm2 <- (lm(`Area harvested`~ CO2_emissions_kt +  I(CO2_emissions_kt^2) + t,  flaxseed_co2_data)) 
summary(lm2)

```


As c02 emission increases the area harvested decreases. This allows us to create an ACF model. We will be adjusting the model to show autocorrelation. P values are statistically significant and there strong positive relationship. 



```{r}
flaxseed_co2_data %>% mutate(y_fit = predict(lm2)) %>% ggplot(aes(x = `Area harvested`, y = y_fit)) + geom_point()+ geom_smooth(method="lm")
#predicted 400, and true value is 200. 
#lag of harvest data, and co2 emission
#prediction aganist the real value of area harvested. The point needs to be aligned and 45 degrees. 
lm2 <- (lm(`Area harvested`~ lag(CO2_emissions_kt) +  I(lag(CO2_emissions_kt)^2) + t,  flaxseed_co2_data)) 
summary(lm2)
y_pred <- flaxseed_co2_data %>% select(`Area harvested`,CO2_emissions_kt, t) 
y_pred <-rbind(y_pred, c(NA,NA,33))
y_pred2 <- predict(lm2,y_pred)
flaxseed_pred <- data.frame(y = c(flaxseed_co2_data$`Area harvested`, NA),
                            y_fit= c(y_pred2),
                            Year= c(1990:2022))

flaxseed_pred %>% ggplot()+
  geom_line(aes(x = Year, y = y, color = "Obs"))+
  geom_line(aes(x = Year, y = y_fit, color = "pred")) + labs(y = "Production") + labs(title = "  Prediction Model for Flaxseed" )
flaxseed_pred %>% tail(5)

```

The obs values are in red, and the blue line is the predicted values. We predicted 2022 using the lag of co2 emission in 2021. We were able to predict this because of ACF model, which showed no autocorrelation. The prediction produced is on average close to the observed values. 







